---
title: "Sentiment Analysis Omega 3"
author: "Anna Pankowska"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Pakiety
```{r packages i dane}
libraries <- c("tm", "tidytext", "ggplot2", "wordcloud", "syuzhet", "dplyr", "tibble", "textstem", "textdata", "tidyr", "Matrix", "topicmodels", "stringr", "reshape2", "LDAvis", "jsonlite")
for (lib in libraries) { 
  library(lib, character.only=TRUE) #Library takes function names without quotes, character only must be used in a loop of this kind.
}
```
#THE NAMES OF SOME VARIABLES ARE WRITTEN IN POLISH, WHICH MADE THE ANALYSIS EASIER FOR ME
#TO FACILITATE UNDERSTANDING OF THE CODE, COMMENTS HAVE BEEN ADDED IN ENGLISH


#Loading data
```{r Load Dataset}
filepath<-"C:\\Users\\Ania\\OneDrive - University of South Wales\\Documents\\Supplement Data Omega 3.csv"
#Define file path. Windows requires \ to be replaced by \\.Works on Mac (apparently).

df<-as_tibble(read.csv(filepath, stringsAsFactors=FALSE))
#Since we have text data we do not want this read as a factor.

#Inspect summary and first few rows of data.
print(summary(df))
print(head(df))
df %>%
  select(REVIEW)
```
#EDA
```{r EDA}
#Number of reviews for each product
df %>%
  group_by(BRAND) %>%
  summarise(number_of_reviews=n()) %>%
  arrange(desc(number_of_reviews))

#Tokenisation
df_tok_reviews<-df %>%
  unnest_tokens(output=word,input="REVIEW",token="words",to_lower = TRUE)

print(df_tok_reviews)
print(summary(df_tok_reviews))
word_counts_df1<-df_tok_reviews %>%
  count(word,sort=TRUE)

#Common words in reviews
ggplot(word_counts_df1[1:10,],aes(x=reorder(word,n),y=n))+
  geom_col(fill="blue")+
  labs(x="Words",y="Frequency")+
  coord_flip()+
  theme_minimal()


#Average rating for each supplement
average_rating_eda <-df %>%
  group_by(BRAND) %>%
  summarise(mean_rating_eda=mean(RATING,na.rm=TRUE)) %>%
  arrange(desc(mean_rating_eda))
average_rating_eda

wordcloud(words=word_counts_df1$word,freq =word_counts_df1$n,min.freq = 50,random.order = FALSE,random.color = FALSE,color=sample(colors(),size=10))



#Number of duplicated reciews for each product
duplicates_check<-df %>%
  group_by(BRAND) %>%
  summarise(duplicates=sum(duplicated(REVIEW)))%>%
  arrange(desc(duplicates))
duplicates_check
```





#Choosing important information
```{r column selection}
df_selected<- df[,c(1,2,9,10,13,14)]      #Column selection

df_selected %>%
  group_by(BRAND) %>%
  summarise(liczba_recenzji=n()) %>%
  arrange(desc(liczba_recenzji))
  

print(summary(df_selected))

head(df_selected)
```



#Cleaning
#Removing duplicates within a product
```{r Removing duplicates}

dane_bez_duplitatow <- df_selected %>%      #data_withouot_duplicaates
  group_by(BRAND) %>%
  distinct(REVIEW, .keep_all = TRUE) %>%
  ungroup()


print(summary(dane_bez_duplitatow))

dane_bez_duplitatow %>%
  group_by(BRAND) %>%
  summarise(liczba_recenzji=n()) %>%
  arrange(desc(liczba_recenzji))
  



```


# 2 Converting to lowercase
```{r lowercase}

dane_bez_duplitatow$REVIEW <- tolower(dane_bez_duplitatow$REVIEW)
dane_bez_duplitatow %>%
  select(REVIEW)
```

# 3 Removing special characters, numbers, emojis, links and HTML tags

```{r removing special characters}

dane_bez_duplitatow$REVIEW <- dane_bez_duplitatow$REVIEW %>%
  str_replace_all("<[^>]+>", " ") %>%                                         #html
  str_replace_all("http[s]?://\\S+|www\\.\\S+", " ") %>%                      #links
  str_replace_all("[^\\p{L}\\s]", " ") %>%                                    #special chaaracters and emojis
  str_replace_all("\\d+", " ") %>%                                            #numbers
  str_squish()                                                                #spaces
```


# 4 Rmoving empty reviews 
```{r empty reviews}
dane_gotowe_do_tokenizacji<-na.omit(dane_bez_duplitatow)      #data_prepared_for_tokenization
 
dane_gotowe_do_tokenizacji %>%
  select(REVIEW)
print(summary(dane_gotowe_do_tokenizacji))







#Checking if all supplements have at least 100 reviews
dane_gotowe_do_tokenizacji %>%
  count(BRAND,name="liczba_reviews") %>%                                           #liczba_reviews = number_o_reviews
  mutate(perc=round(100 * liczba_reviews /sum(liczba_reviews), 1)) %>%
  arrange(desc(liczba_reviews))

#Removing the supplemets 'Seven Seas' (<100 reviews)
dane_gotowe_do_tokenizacji<-dane_gotowe_do_tokenizacji %>%
  filter(BRAND !="Seven seas")
  
dane_gotowe_do_tokenizacji %>%
  count(BRAND,name="liczba_reviews") %>%
  mutate(perc=round(100 * liczba_reviews /sum(liczba_reviews), 1)) %>%
  arrange(desc(liczba_reviews))

#Total number of reviews
dane_gotowe_do_tokenizacji %>%
  summarise(liczba_reviews=n())
```


# 5 Tokenization: Splitting into individual words (tokens)
```{r tokenization}

tokenized_reviews<-dane_gotowe_do_tokenizacji %>%
  unnest_tokens(output=word,input="REVIEW",token="words",to_lower = TRUE)

word_counts<-tokenized_reviews %>%
  count(word,sort=TRUE)

ggplot(word_counts[1:10,],aes(x=reorder(word,n),y=n))+
  geom_col(fill="blue")+
  labs(x="Words",y="Frequency")+
  coord_flip()+
  theme_minimal()


```

# 6 Stop words
```{r removing stop words}
clean_tokenised_reviews <-tokenized_reviews %>%
  anti_join(stop_words,by="word")

data("stop_words")
unique(stop_words$lexicon)





#Number reviews after cleaning for each product
clean_tokenised_reviews %>% 
  group_by(BRAND) %>%
  summarise(reviews_after_cleaning=n_distinct(ID)) %>%
  arrange(desc(reviews_after_cleaning))

#Total number reviews after cleaning
total_reviews_after_cleaning<-
clean_tokenised_reviews %>%
  summarise(total_reviews=n_distinct(ID))

total_reviews_after_cleaning
```

#Average total rating 
```{r rating}
clean_tokenised_reviews %>%
  count(BRAND,name="liczba_tokenow") %>%                                    #liczba_tokenow = number_of_tokens
  mutate(perc=round(100 * liczba_tokenow /sum(liczba_tokenow), 1)) %>%
  arrange(desc(liczba_tokenow))

#average total rating
average_rating <-clean_tokenised_reviews %>%
  group_by(BRAND) %>%
  summarise(mean_rating=mean(RATING,na.rm=TRUE)) %>%
  arrange(desc(mean_rating))


print(summary(average_rating))
print(average_rating)
```

# 7 Lemmatization (textstem package) 
```{r resorting words to their root forms}
clean_tokenised_reviews <-tokenized_reviews %>%
  anti_join(stop_words,by="word")

clean_tokenised_reviews$word<-gsub("[^a-zA-Z]", " ",clean_tokenised_reviews$word) %>%
  na_if(" ") %>%
  lemmatize_words()

clean_tokenised_reviews<-na.omit(clean_tokenised_reviews)

print(summary(clean_tokenised_reviews))
print(clean_tokenised_reviews)
clean_tokenised_reviews %>%
  distinct(BRAND,ID) %>%
  count(BRAND,name="review_count")

print(clean_tokenised_reviews)
```

# 8 Visualisation
```{r wyswietlenie}
word_counts<-clean_tokenised_reviews %>%
  count(word,sort=TRUE)

top_words<-top_n(word_counts,10,n)$word

filtered_word_counts<-filter(word_counts,word%in%top_words)
filtered_word_counts$word<-factor(filtered_word_counts$word,levels = top_words[length(top_words):1])

ggplot(filtered_word_counts,aes(x=reorder(word,n),y=n))+
  geom_col(fill="blue")+
  labs(x="Words",y="Frequency")+
  coord_flip()+
  theme_minimal()

set.seed(2)
wordcloud(words=word_counts$word,freq =word_counts$n,min.freq = 50,random.order = FALSE,random.color = FALSE,color=sample(colors(),size=10))
```


# 9 Grouping the most frequent tokens by brand
```{r top tokens per brand}
grouped_count<- group_by(clean_tokenised_reviews,BRAND) %>%
  count(word) %>%
  filter(word %in% top_words)

grouped_count$word <-factor(grouped_count$word,levels=top_words[length(top_words):1])             #orders the top words according to overall frequency

ggplot(data=grouped_count,aes(x=word,y=n,fill=BRAND))+
  geom_col(position = "dodge")+
  labs(x="Words",y="Fill",fill="BRAND")+
  coord_flip()+
  theme_minimal()

```







#SENTIMENT ANALYSIS
# 2 lexicons: afinn and bing
```{r loading lexicons}
afinn<-get_sentiments("afinn")
bing<-get_sentiments("bing")

```


# Sentimenet Afinn for each review
```{r Afinn for each review}
#clean_tokenised_reviews
#Afinn
clean_tokenised_reviews_with_sent_afinn<-clean_tokenised_reviews %>%
  inner_join(afinn, by="word")
# afinn for each review  
afinn_sent_review<-clean_tokenised_reviews_with_sent_afinn%>%
  group_by(ID) %>%
  summarise(mean_afinn_sentiment=mean(value, na.rm=TRUE))%>%
  ungroup()
  
data_with_sent_afinn_review<-clean_tokenised_reviews_with_sent_afinn%>%
  select(ID, BRAND, EPA..DHA, PRICE.in.., RATING) %>%
  distinct(ID, .keep_all = TRUE) %>%
  arrange(ID)
data_with_sent_afinn_review


afinn_sent_review<-afinn_sent_review%>%
  right_join(data_with_sent_afinn_review, by="ID")

#normalization
afinn_sent_review<-afinn_sent_review%>%
  select(ID, BRAND, EPA..DHA, PRICE.in.., RATING,mean_afinn_sentiment) %>%
  mutate(normalised_sentiment_score=(mean_afinn_sentiment+5)/10)


afinn_sent_review

#afin: distribution after normalization
ggplot(afinn_sent_review,aes(x=normalised_sentiment_score))+
  geom_histogram(binwidth = 0.1)
```


#Dominant sentiment based on all reviews
```{r Overall sentiment }
#average overall sentiment
overal_sent<-mean(afinn_sent_review$normalised_sentiment_score, na.rm=TRUE)
print(overal_sent)

#median
median_token_sent<-median(afinn_sent_review$normalised_sentiment_score, na.rm=TRUE)
print(median_token_sent)



#Afinn sentiment for each supplement
brand_sentiment_normal<-afinn_sent_review%>%
  group_by(BRAND)%>%
  summarise(average_brand_normalised_sentiment=mean(normalised_sentiment_score, na.rm=TRUE))%>%
  arrange(desc(average_brand_normalised_sentiment))
print(brand_sentiment_normal)

ggplot(brand_sentiment_normal,aes(x=reorder(BRAND,average_brand_normalised_sentiment),y=average_brand_normalised_sentiment,fill=BRAND))+
  geom_bar(stat = "identity")+
  coord_flip()+
  labs(title="Average Sentiment Score for Each Supplement",x="BRAND",y="Average sentiment Score")

afinn_sent_review<-afinn_sent_review%>%
  right_join(brand_sentiment_normal, by="BRAND")
afinn_sent_review

```


# RQ1
```{r RQ1}
#data for RQ1 
do_korelacji_pyt1<-afinn_sent_review %>%                                          #do_korelacji_pyt1 = for_correlation_of_RQ1
  group_by(BRAND,PRICE.in..,EPA..DHA,average_brand_normalised_sentiment)%>%
  summarise(average_rating=mean(RATING,na.rm=TRUE))
print(do_korelacji_pyt1)


#Price
#correlation 
spearman_price<-cor.test(do_korelacji_pyt1$average_brand_normalised_sentiment, do_korelacji_pyt1$PRICE.in.., method="spearman")
spearman_price
#visualization
ggplot(do_korelacji_pyt1,aes(x=PRICE.in..,
                          y=average_brand_normalised_sentiment))+
  geom_point(alpha=0.3)+
  geom_smooth(method = "",se=FALSE,color="blue")+
  labs(title="Price vs. Sentiment Score",
       x="Price (£)",
       y="Sentiment Score")+
  theme_minimal()



#amount of acids in the product
#correlation
spearman_ilosc_kwasow<-cor.test(do_korelacji_pyt1$average_brand_normalised_sentiment, do_korelacji_pyt1$EPA..DHA, method="spearman")
spearman_ilosc_kwasow
#visualization
ggplot(do_korelacji_pyt1,aes(x=EPA..DHA,
                          y=average_brand_normalised_sentiment))+
  geom_point(alpha=0.3)+
  geom_smooth(method = "",se=FALSE,color="blue")+
  labs(title="Polyunsaturated Fatty Acids per Sering (mg) vs. Sentiment Score",
       x="EPA+DHA (mg)",
       y="Sentiment Score")+
  theme_minimal()




#review length
policzenie_dlugosci_recenzji<-clean_tokenised_reviews %>%            #policzenie_dlugosci_recenzji = counting_review_length
  group_by(ID) %>%
  summarise(word_count=n(), .groups = "drop")
policzenie_dlugosci_recenzji
#distribution of reiew length
ggplot(policzenie_dlugosci_recenzji,aes(x=word_count))+
  geom_histogram(binwidth = 5,fill="steelblue",color="black")+
  labs(title = "Distribution of the lengths of reviews", x="Review length",y="Number of reviews")


afinn_sent_review<-afinn_sent_review%>%
  left_join(policzenie_dlugosci_recenzji, by="ID")
afinn_sent_review
#correlation  
spearman_dlugosc_recenzji<-cor.test(afinn_sent_review$normalised_sentiment_score, afinn_sent_review$word_count, method="spearman")
spearman_dlugosc_recenzji
#visualization
ggplot(afinn_sent_review,aes(x=word_count,
                          y=normalised_sentiment_score))+
  geom_point(alpha=0.3)+
  geom_smooth(method = "",se=FALSE,color="blue")+
  labs(title="Review length vs. Sentiment Score",
       x="Review length",
       y="Sentiment Score")+
  theme_minimal()

```


#Bing 
```{r wizualizacja}

#Bing
#bing_sent<-clean_tokenised_reviews %>%
  #inner_join(bing, by="word") %>%
# bing dla kazdej recenzji  
#bing_sent_score <-bing_sent %>%
  #mutate(value=ifelse(sentiment=="positive",1,-1)) %>%
  #group_by(ID) %>%
#summarize(bing_sentiment=sum(value))



#bing

#ggplot(bing_sent,aes(x=bing_sentiment))+
#  geom_histogram(binwidth = 1)




```


# RQ 2
# most praised vs. most critized
```{r bing}

tokens_sent<-clean_tokenised_reviews %>%
  inner_join(get_sentiments("bing"),by=c("word"="word"))
word_counts_bing_sent<-tokens_sent %>%
  count(word,sentiment,sort=TRUE)

procenty_pozyt_negat<-tokens_sent%>%                         #procety_pozyt_negat = percentages_positive_negative
  count(sentiment) %>%
  mutate(procent=n/sum(n)*100)
procenty_pozyt_negat

ggplot(tokens_sent,aes(x=sentiment,fill=sentiment))+
  geom_bar()+
  scale_fill_manual(values=c("positive"="green","negative"="red"))+
  geom_text(stat="count", aes(label=..count..),vjust=-0.3)+
  labs(title="Distribution of tokens by sentiment",
       x="Sentiment",
       y="Number of tokens")+
  theme_minimal()







# top 10 positive and top 10 negative
top_positive<-word_counts_bing_sent %>%
  filter(sentiment=="positive") %>%
  top_n(10,n)

top_negative<-word_counts_bing_sent %>%
  filter(sentiment=="negative") %>%
  top_n(10,n)

print(top_positive)
print(top_negative)

top_words<-bind_rows(top_positive %>%
                        mutate(sentiment="Positive"),
                      top_negative %>%
                        mutate(sentiment="Negative")
                      )

ggplot(top_words,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~sentiment,scales="free")+
  coord_flip()+
  labs(title = "Top 10 positive and negative words by frequency", x="Words",y="Frequency")







# 10 top positive and 10 top negative words for each product
bing<-get_sentiments("bing")
clean_tokenised_reviews_bing_all<-clean_tokenised_reviews %>%
  inner_join(bing,by="word") %>%
  count(BRAND,sentiment,word,sort=TRUE) %>%
  group_by(BRAND,sentiment) %>%
  slice_max(order_by = n,n=10,with_ties = FALSE) %>%
  ungroup()

clean_tokenised_reviews_bing_all


# vizualization for each supplement
supplement1<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="EQOLOGY")
ggplot(supplement1,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu EQOLOGY", x="Slowa",y="czestotliwosc")


supplement2<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Horbaach")
ggplot(supplement2,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Horbaach", x="Slowa",y="czestotliwosc")


supplement3<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Igennus")
ggplot(supplement3,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Igennus", x="Slowa",y="czestotliwosc")


supplement4<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Lindes")
ggplot(supplement4,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Lindes", x="Slowa",y="czestotliwosc")


supplement5<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Mollers")
ggplot(supplement5,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Mollers", x="Slowa",y="czestotliwosc")


supplement6<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Nordic Naturals")
ggplot(supplement6,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Nordic Naturals", x="Slowa",y="czestotliwosc")


supplement7<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Nutravita")
ggplot(supplement7,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Nutravita", x="Slowa",y="czestotliwosc")


supplement8<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="VITABIOTICS")
ggplot(supplement8,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu VITABIOTICS", x="Slowa",y="czestotliwosc")


supplement9<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="WeightWorld")
ggplot(supplement9,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu WeightWorld", x="Slowa",y="czestotliwosc")


supplement10<-clean_tokenised_reviews_bing_all %>%
  filter(BRAND=="Zipvit")
ggplot(supplement10,aes(x=reorder(word,n),y=n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_grid(BRAND~sentiment,scales="free")+
  labs(title="Top 10 pozytywnych i negatywnych slow dla suplementu Zipvit", x="Slowa",y="czestotliwosc")





```


#RQ 4
```{r correlation: rating vs. sentiment}
print(afinn_sent_review)
spearman_rating_vs_sent<-cor.test(afinn_sent_review$normalised_sentiment_score, afinn_sent_review$RATING, method="spearman")
spearman_rating_vs_sent

barplot(table(afinn_sent_review$RATING),
        main="Distribution of Ratings",
        xlab="Rating",
        ylab="count",
        col="skyblue")

mean(afinn_sent_review$RATING, na.rm=TRUE)
median(afinn_sent_review$RATING, na.rm=TRUE)
sum(afinn_sent_review$RATING==5)
procent_5<-sum(afinn_sent_review$RATING==5)/nrow(afinn_sent_review)*100
procent_5



#visualization
ggplot(afinn_sent_review,aes(x=RATING,
                          y=normalised_sentiment_score))+
  geom_jitter(width = 0.2, alpha=0.5,color="darkblue")+
  geom_smooth(method = " ")+
  labs(title="Rating vs Sentiment for Each Review",
       x="Rating",
       y=" Sentiment")+
  theme_minimal()






#BRAND
brand_sentiment_normal<-brand_sentiment_normal%>%
  right_join(average_rating, by="BRAND")
brand_sentiment_normal 

ggplot(do_korelacji_pyt1,aes(x=average_rating,
                          y=average_brand_normalised_sentiment))+
  geom_point(alpha=0.3)+
  geom_smooth(method = "",se=FALSE,color="blue")+
  labs(title="Sentiment Scores vs Ratings Across Supplements ",
       x="Rating",
       y="Sentiment Score")+
  theme_minimal()
spearman_rating_sent_per_brand<-cor.test(brand_sentiment_normal$average_brand_normalised_sentiment, brand_sentiment_normal$mean_rating, method="spearman")
spearman_rating_sent_per_brand








```





#RQ3
# Topics discussed in reviews
```{r topic modelling}
print(clean_tokenised_reviews)

 
clean_tokenised_reviews_combined<-clean_tokenised_reviews %>%
  group_by(ID, BRAND,RATING) %>%
  summarise(REVIEW=paste(word,collapse= " "))
head(clean_tokenised_reviews_combined)


df1<-clean_tokenised_reviews_combined %>%
  select(BRAND,RATING,REVIEW) %>%
  filter(str_count(REVIEW)>=100 & str_count(REVIEW)<=500)
print(summary(df1))


df1$Review_no<-1:nrow(df1)
if(nrow(df1)>1000){
  set.seed(3)
  df1<-sample_n(df1,1000)
}
print(summary(df1))




#creating tdm
#converting text into a corpus
corpus<-Corpus(VectorSource(df1$REVIEW))
tdm<-TermDocumentMatrix(corpus)
tdm_matrix<-as.matrix(tdm)



#most frequent and rare occurring word
frequent_terms<-findFreqTerms(tdm,lowfreq = 0.1*ncol(tdm_matrix))
rare_terms<-findFreqTerms(tdm,highfreq = 0.01*ncol(tdm_matrix))
print(frequent_terms)
print(rare_terms)


to_keep<-c(" ")
to_remove<-frequent_terms[!frequent_terms %in% to_keep]


filtered_tdm_matrix<-tdm_matrix[!rownames(tdm_matrix) %in% to_remove, ]
filtered_tdm_matrix<-filtered_tdm_matrix[!rownames(filtered_tdm_matrix) %in% rare_terms, ]

column_sums<-colSums(filtered_tdm_matrix)

zero_columns<-which(column_sums==0)
if(length(zero_columns)>0){
  filtered_tdm_matrix<-filtered_tdm_matrix[, -zero_columns]
}else{
  print("No zero columns in TDM matrix")
}

term_frequencies<-rowSums(filtered_tdm_matrix)

term_frequency_df1<-data.frame(term=names(term_frequencies),frequency=term_frequencies)

top_terms<-term_frequency_df1 %>%
  arrange(desc(frequency)) %>%
  head(10)

print(top_terms)


#create histogram
ggplot(term_frequency_df1,aes(x=frequency))+
  geom_histogram(binwidth = 1)+
  labs(title="Histogram of Term Frequencies", x="Term Frequency", y="Number of Terms")+
  theme_minimal()



num_freq<-length(frequent_terms)
num_freq
num_rare<-length(rare_terms)
num_rare
total_terms<-nrow(tdm_matrix)
total_terms

#percentage
percent_freq<-(num_freq/total_terms)*100
percent_freq
percent_rare<-(num_rare/total_terms)*100
percent_rare


```


#LDA model
```{r LDA model}
set.seed(5)
dtm<-t(filtered_tdm_matrix)

lda_model<-LDA(dtm,k=2,control=list(seed=5))
lda_model

topics<-tidy(lda_model,matrix="beta")
topics

top_terms<-topics %>%
  group_by(topic)%>%
  top_n(10,beta)%>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms %>%
  ggplot(aes(x=reorder(term,beta),y=beta,fill=factor(topic)))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~topic,scales="free")+
  coord_flip()
           


range_k<-seq(2,10,by=1)
perplexities<-sapply(range_k,function(k){
  set.seed(5)
  model<-LDA(dtm,k=k,control = list(seed=5))
  perplexity(model)
})

#perplexities
plot(range_k,perplexities,type="b",xlab="number of topics", ylab="perplexity")




#final model
dtm<-t(filtered_tdm_matrix)
lda_model<-LDA(dtm,k=3,control=list(seed=5))
#lda_model

topics<-tidy(lda_model,matrix="beta")
topics

top_terms<-topics %>%
  group_by(topic)%>%
  top_n(10,beta)%>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms %>%
  ggplot(aes(x=reorder(term,beta),y=beta,fill=factor(topic)))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~topic,scales="free")+
  coord_flip()

```

```{r LDA model}
set.seed(5)
lda_model <- LDA(dtm, k = 3)
lda_vis_data <- createJSON(phi = posterior(lda_model)$terms,
                          theta = posterior(lda_model)$topics,
                          doc.length = rowSums(as.matrix(dtm)),
                          vocab = colnames(as.matrix(dtm)),  
                          term.frequency = colSums(as.matrix(dtm)))
serVis(lda_vis_data)

```





